---
title: "Assessment3"
author: "Chi WAN"
date: "08/11/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
ikea <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-11-03/ikea.csv')
```
```{r}
## Price, remove the no old price
ikea<-ikea %>%
  mutate(old_price= parse_number(old_price))
```
# Chi Him Wan part
# Chi Him Wan part
# Chi Him Wan part



## Executive Summary
```{r}
## Product are not sellable online
ikea%>%
  filter(sellable_online=="FALSE")
```

```{r}
## count category
ikea%>%
  count(category,sort = TRUE)
```
```{r}
ikea %>%
  add_count(category) %>%
  mutate(category_fct = fct_reorder(category, n)) %>%
  ggplot(aes(x = category_fct)) +
  geom_bar() +
  geom_text(aes(label = n, y = n), nudge_y = 30)+
  coord_flip() +
  theme_minimal() +
  labs(x = "Items",
       y = "Number",
       title = "Category")
```
```{r}
## create a new variable for discount = Old price - Price
ikea<-ikea%>%
  mutate(discount=100-price/old_price*100)
```
```{r}
ikea%>%
  count(designer, sort = TRUE)
```






```{r}
ikea %>%
  add_count(designer) %>%
  mutate(designer_fct = fct_reorder(designer, n)) %>%
  ggplot(aes(x = designer_fct)) +
  geom_bar() +
  geom_text(aes(label = n, y = n), nudge_y = 30)+
  coord_flip() +
  theme_minimal() +
  labs(x = "3",
       y = "2",
       title = "1")
```
```{r}
## How is the price relaed to the furniture dimensions?
ikea%>%
  count(other_colors,sort = TRUE)
```

```{r}
##The most expensive furniture on average is ???? with an average price of $???
ikea <- ikea%>%
  group_by(category)%>%
  mutate(average_price = mean(price))%>%
  ungroup()
ikea%>%
  select(sellable_online,category,average_price)
ikea%>%gather(category,"Bar furniture","average_price",1:2)
  
##are they sellable online and most of them have other color option?
ikea <- ikea%>%
  group_by(sellable_online)%>%
  mutate(colours_available = (other_colors))
ikea%>%
  count(colours_available)
```
```{r}
ikea %>%
  ggplot(aes(x=average_price, y=category)) + 
  geom_bar(stat="identity", fill="red") + 
  labs(title="Average Price by each category", 
       subtitle="Ikea") + 
  theme()
```

# Van Nhan Cao part
# Van Nhan Cao part
# Van Nhan Cao part

```{r}
#number of not online sellable items
ikea%>%
  count(sellable_online,sort = FALSE)
```
We count the number of items that are not sellable online items, which is 28 items
```{r}
#Count the not sellable items having discount price  
ikea%>%filter(sellable_online=="TRUE")%>%count(old_price)  
```

```{r}
#Count the not sellable items having discount price  
ikea%>%filter(sellable_online=="FALSE")%>%count(old_price)  
```



We count the number of not sellable online items having the discount price. From that result, we have a ratio between the not sellable online items/ sellable online items= 2/3014. 

```{r}
## create a new variable for discount = Old price - Price
ikea<-ikea%>%
  mutate(discount=100-price/old_price*100)
```
With the new variable, we can calculate the variance between the old price and current price. This variable will be useful to identify how good its consumption of items can be
```{r}
#rank the level of consumption for every items
ikea<-ikea%>%
  mutate(rating_discount= as.factor(
    case_when(discount >= 20 ~"Dissatisfied",
              discount >=10 ~"Considerable",
    discount<10 ~ "Acceptable",
   
    
 
     )
  )
  )


```
Basing on the variable of discount, We create the new variable which is rating_discount to rank the level of consumption for every items
After the classification, we can see that 3040 items of IKEA furniture meet the sale target because they don't have the discount. 
However, 394 items of IKEA furniture did not meet the sales target. 
The items do not have old_price or its discount below 10% meaning that consumptions have good turnover so we keep selling them with current price.
The items having the discount above 10-20% show that they have good profit but probably out of season or we need to sell them quickly to prepare for next season.
The items having the discount above 20% show that they have unacceptable profit bc of out of season, not trendy anymore
so it cannot satisfy the stakeholders. 

```{r}
#count the amount of items in every levels  
ikea%>%count(rating_discount)
```



```{r}
ikea %>%
  add_count(rating_discount) %>% arrange(desc(n))%>%
  mutate(rating_discount_fct = fct_reorder(rating_discount, n)) %>%
  ggplot(aes(x = rating_discount_fct)) +
  geom_bar() +
  geom_text(aes(label = n, y = n), nudge_y = 40)+
  coord_flip() +
  theme_minimal() +
  labs(x = "Level of Rating",
       y = "Number",
       title ="Standard")
```
As we can see from the chart after classifying the level of consumption target that an item can reach, we have 3040 items reach 'NA'~ Satisfied revenue, 132 commodities have acceptable consumption, 128 goods reach considerable goal and 394 items reach the target of dissatisfaction.

# Check category to find out which types have bad performance.


```{r}
Designer<- ikea%>%select(category,rating_discount)
```
```{r}
Huy<- Designer%>%select(category,rating_discount)%>%filter(rating_discount %in% c("Dissatisfied"))%>%count(category)%>% arrange(desc(n))
```
```{r}
Huy %>%
  add_count(category) %>% arrange(desc(n))%>%
  mutate(category_fct = fct_reorder(category, n)) %>%
  ggplot(aes(x = category_fct)) +
  geom_bar() +
  geom_text(aes(label = n, y = n), nudge_y = 30)+
  coord_flip() +
  theme_gray() +
  labs(x = "Category",
       y = "Number",
       title ="Dissatisfied items")

```

From that chart, we found out that Sofas and armchairs have the most items having dissatisfied consumption when its number is 96, double the second follower which is Chests of drawers & drawer units. Wardrobes and Tables & desks come third and fourth with 42 and 39 items having dissatisfied revenue.
On the other hand, Sideboards, buffets & console tables has the smallest number of items having bad profit with 1 items. Furthermore, both Trolleys, room dividers and nursery furniture come second with 2 items



```{r}
Nhan<- ikea%>%select(designer,rating_discount)
```

```{r}
# Check which designers have most bad performance's items
Nhan1<- Nhan%>%select(designer,rating_discount)%>%filter(rating_discount %in% c("Dissatisfied"))%>%count(designer)%>% arrange(desc(n))
```


```{r}
Nhan1 %>%
  add_count(designer) %>% arrange(desc(n))%>%
  mutate(designer_fct = fct_reorder(designer,n)) %>%
  ggplot(aes(x = designer_fct)) +
  geom_bar() +
  geom_text(aes(label = n, y = n), nudge_y = 30)+
  coord_flip() +
  theme_gray() +
  labs(x = "Designer",
       y = "Number",
       title ="Which designer have most dissatisfied items")

```
Ola Wihlborg is the designer who has worst performance when 63 items have dissatisfied consumption. IKEA of Sweden comes second with 39 items and Ehlen Johansson comes third with 37 items.
On the other hand, 
```{r}
# create new variable of dimension
ikea<-ikea%>%
  mutate(Totalsize= height*width*depth)%>% na.omit(height,width,depth)
    
``` 
From the dataset of three variables including height, width and depth, we create a new variable which is Total_size. That is the dimension of item could be with the formula: Totalsize= height* width *depth




```{r}
## indentify the type of variables
ikea%>%
sapply(.,class)
```

```{r}
## Assumption: examine the relationship between the dimension of furniture with the discount price of item
ikea %>% 
  lm(discount ~ Totalsize, data = .) %>%
  summary()
```
p- value = how significant is the variable•p-value of the coefficients:***:  predictor is meaningful for our model
R2=Explained Variation of the model/ Total variation of the model
•Models that poorly fit the data have R² near 0.
•As you can see, the first one has an R² of 0.01; this means that the model explains only 1% of the data variability

#Findings:
Briefly, the current business runs well when just around 10% of total items dissatisfied the expectation of stakeholders about the consumption, meanwhile over 80% of items reach target. Furthermore, we found out that there is no correlation between the dimension of furniture with the discount of price, which means that the total dimension of product is not the characteristic that impact the decision of the customers.  Finally, the limitation of not online sellable items does not affect the business of IKEA when those not sellable online products having discount price just account for the minority of total items.
#Recommendation:

From our perspective, after having some findings from the data of IKEA, although IKEA is doing well, they still have many things to do to sustain its business. Reduce importing and manufacturing the items having dissatisfied consumption is one of their preferences to maximize their profit. They can launch more promotion with items having considerable consumption to reach the target of profit as well as clear the inventory for next season items. On the other hand, with the items having satisfied and acceptable profits, IKEA executives should have policies to encourage its designers continue creating more great products in the futures such as giving them financial bonus. Moreover, the executives should consider terminating the contract with Ola Wihlborg’s designer, giving a critical review with the marketing team who collaborate with them because of the poor performance of 63 out of 134 their product as well as creating a good condition for designers whose products have good consumption. Finally, the not sellable online product prove that they have good performance though the online limitation. The Board should consider make it visible on online website so more customers can view it without going to store and can increase its profit, especially during COVID-19.
#Conclusion
In a nutshell, a steady development of the Ikea retail business appears to be the focus for the company in the near future, with strategies unlikely to include aggressive expansion into new areas, especially the sector of e-commerce, making shopping at Ikea more accessible, may also have a positive impact on sales, although no progress has been visible on this front of late, and as such Ikea has been very guarded over its profit levels. Moreover, through this report, we hope that IKEA will take actions to manage the list of items that they are having to have a profit that is as good as possible. 
